Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-11-30 rCode/Draft.Rmd
last updates

### 1. Figure 1: Manufacturing Layoffs Over Time

### Nationwide Manufacturing Layoffs Per Worker, 1995-2019

@@

ggplot(data = national_ts %>% filter(Year >= 1995), aes(x = Year, y = `Job Change per Worker`)) +
  geom_col() + scale_x_continuous(breaks=seq(1995,2019,2)) +
	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6)) +
  labs()

@@

### Geographic Concentration of Layoffs

@@

state_shape <- states(
  cb = TRUE,
  resolution = "20m",
  progress_bar = F
) %>%
  filter(GEOID != "72") %>%
  shift_geometry()

@@

labels = c(
  "1" = "1% or Greater Gain in Mfg. Emp",
  "2" = "0% to 1% Gain in Mfg. Emp",
  "3" = "0% to 1% Loss in Mfg. Emp",
  "4" = "1% to 3% Loss in Mfg. Emp",
  "5" = "3% to 6% Loss in Mfg. Emp",
  "6" = "6% or Greater Loss in Mfg. Emp")

@@

ggplot() +
  geom_sf(data = mapping_county, aes(fill = ntile_mfg), 
          color = NA, size = .01) +
  scale_fill_manual(values = colors,
                    labels = labels) +
  # add state lines
  geom_sf(data = state_shape, fill = NA, color = "black", size = .1) +
  coord_sf(datum = NA) +
  theme_minimal() +
  # geom_sf_text_repel(aes(label = state), data = mapping_small,
  #                    force = .00001,  seed = 10,
  #                    size = 2.5) +
  theme(  axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          text = element_text(size = 8)) + 
  labs(title = "Figure X:\nNet Change in Manufacturing Employment from 2004 to 2015",
       subtitle = "Normalized by 2004 Overall Employment Levels",
       fill = "Cumulative Change in Manufacturing\nEmployment (2004-2015) per\n2004 Worker")

@@

### Descriptive Statistics
```{r,  echo=F}
descriptiveData <-  readRDS("../tableData.rds")

@@

## Figures

### Regression summaries

@@

@@

### Counterfactual assessment of election
## (Using 2004-2015 Layoffs)

@@

# create mapping categories
order = c(
  "+2% or greater", 
  "+1% to +2%",
          "+0.5% to +1%",
          "+0.25% to +0.5%", 
          "0% to +0.25%", 
          "0% to -0.25%")

@@

colors =
   c(
     "+2% or greater" = "#0059ff",
     "+1% to +2%" = "#4988fc",
     "+0.5% to +1%" = "#86b0fc",
     "+0.25% to +0.5%" = "#b8d1ff",
     "0% to +0.25%" = "#dee9fc",
     "0% to -0.25%" = "#ffeae8")

@@

#  make map
flipped <- mapping_small %>% filter(changed_outcome == "Yes")
ggplot() +
  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "grey", size = .01) +
  scale_fill_manual(values = colors) +
  labs(title = "Figure X:\nWithout Manufacturing Layoffs, Democrats Would Have Won 2016 Election",
       subtitle = "Change in Democratic Vote Share Assuming Counterfactual Manufacturing Layoffs (25th Percentile)",
       fill = "Change in Democratic Vote Share") +
  geom_sf(data = flipped, fill = NA, aes(color = changed_outcome), size = 1) +
  scale_color_manual(values = "#b32ab5", name = "Flipped Election") +
  labs(color = "Flipped Election") +
  coord_sf(datum = NA) +
  theme_minimal() +
  # geom_sf_text_repel(aes(label = state), data = mapping_small,
  #                    force = .00001,  seed = 10,
  #                    size = 2.5) +
  theme(  axis.title.x=element_blank(),
          axis.title.y=element_blank())

>>>>

### Manufacturing Layoffs Over Time

@@

ggplot(data = national_ts %>% filter(Year >= 1995), 
       aes(x = Year, y = `Job Change per Worker`)) +
  ylab("Millions of Jobs") +
  ggtitle("Figure 1. Nationwide Change in Manufacturing Employment, 1995-2019") +
  geom_col(fill = "#4287f5") + scale_x_continuous(breaks=seq(1995,2019,2)) +
	scale_y_continuous(labels = label_number(suffix = "", scale = 1e-6)) +
  theme_minimal()

@@

\newpage
### Geographic Concentration of Layoffs

@@

state_shape <- states(
  cb = TRUE,
  resolution = "20m",
  progress_bar = F
) %>%
  filter(GEOID != "72" & GEOID != "02", GEOID != "15")

@@

labels = c(
  "1" = "1% or Greater Gain",
  "2" = "0% to 1% Gain",
  "3" = "0% to 1% Loss",
  "4" = "1% to 3% Loss",
  "5" = "3% to 6% Loss",
  "6" = "6% or Greater Loss")

@@

ggplot() +
  geom_sf(data = mapping_county, aes(fill = ntile_mfg), 
          color = NA, size = .01) +
  scale_fill_manual(values = colors,
                    labels = labels) +
  # add state lines
  geom_sf(data = state_shape, fill = NA, color = "black", size = .1) +
  coord_sf(datum = NA) +
  theme_minimal() +
  # geom_sf_text_repel(aes(label = state), data = mapping_small,
  #                    force = .00001,  seed = 10,
  #                    size = 2.5) +
  theme(  axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          text = element_text(size = 8)) + 
  labs(title = "Figure 2: Net Change in Manufacturing Employment from 2004 to 2015",
       subtitle = "Normalized by 2004 Overall Employment Levels",
       fill = "Cumulative Change in Manufacturing\nEmployment (2004-2015) per\n2004 Worker")

@@

\newpage
### Descriptive Statistics
```{r,  echo=F}
descriptiveData <-  readRDS("../tableData.rds")

@@

\newpage
### Regression Results (Using 2004-2015 Net Manu Job Change)

@@

\newpage
### Regression Results (Using 2012-2015 Net Manu Job Change)

@@

\newpage
### Counterfactual assessment of election (Using 2004-2015 Layoffs)

```{r,  echo=F, message = F}

@@

# create mapping categories
order = c(
 # "+2% or greater", 
  #"+1% to +2%",
          "+0.5% to +1%",
          "+0.25% to +0.5%", 
          "0% to +0.25%", 
          "0% to -0.25%")

@@

colors =
   c(
    # "+2% or greater" = "#0059ff",
     #"+1% to +2%" = "#4988fc",
     "+0.5% to +1%" = "#86b0fc",
     "+0.25% to +0.5%" = "#b8d1ff",
     "0% to +0.25%" = "#dee9fc",
     "0% to -0.25%" = "#ffeae8")

@@

#  make map
flipped <- mapping_small %>% filter(changed_outcome == "Yes")
ggplot() +
  geom_sf(data = mapping_small, aes(fill = delta_vs_group), color = "black", size = .1) +
  scale_fill_manual(values = colors) +
  labs(title = "Figure 3: Impact of Manufacturing Job Lossess on Democratic Vote Share",
       subtitle = "Change in Democratic Vote Share Assuming 25th Percentile of Manufacturing Job Losses",
       fill = "Change in Democratic Vote Share") +
  geom_sf(data = flipped, fill = NA, 
          aes(color = changed_outcome), 
          size = 1) +
  scale_color_manual(values = "#b32ab5", name = "Flipped Election") +
  labs(color = "Flipped Election") +
  coord_sf(datum = NA) +
  theme_minimal() +
  # geom_sf_text_repel(aes(label = state), data = mapping_small,
  #                    force = .00001,  seed = 10,
  #                    size = 2.5) +
  theme(  axis.title.x=element_blank(),
          axis.title.y=element_blank())
